\documentclass[12pt]{article}
\pagestyle{plain}

\oddsidemargin  -0.5 cm
\evensidemargin 0 cm
\textwidth      6.5in
\headheight     0.0in
\topmargin      -1 cm
\textheight=9.0in

\begin{document}

\begin{center}
  \begin{tabular}{p{4.5 cm} p{1.5 cm} p{4.5 cm}}
    \begin{minipage}{\linewidth}
      \begin{center}
	{\bf \large Jim Pivarski} \\
	(607) 254 2774 \\
	mccann@lepp.cornell.edu
      \end{center}
    \end{minipage} & &
    \begin{minipage}{\linewidth}
      Wilson Laboratory \\
      Cornell University \\
      Ithaca, NY 14853-8001
    \end{minipage}
  \end{tabular}
\end{center}

\subsubsection*{Research Interests}

I am excited by the potential for discovery in the interface between
particle physics and cosmology, and would like to take advantage of
this turning point in my life to pursue a career in that field.

\subsubsection*{Education}

\begin{itemize}

  \item Ph.\ D.\ in Physics, Cornell University, expected December 2005

    (Courses included Quantum Field Theory, Cosmology, and an intense
    graduate lab.)

  \item B.\ S.\ in Physics with a minor in Mathematics, Carnegie
    Mellon University, May 1999

\end{itemize}

\subsubsection*{Research Experience}

\begin{itemize}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.65\linewidth}} & \mbox{\hspace{0.315\linewidth}} \vspace{-0.4 cm} \\
Research Assistant in the CLEO Collaboration & Summer 2000 -- present \end{tabular}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.65\linewidth}} & \mbox{\hspace{0.315\linewidth}} \vspace{-0.4 cm} \\
Di-electron Widths ($\Gamma_{ee}$) of $\Upsilon(1S)$, $\Upsilon(2S)$, and $\Upsilon(3S)$ & Advisor: Ritchie Patterson \end{tabular}

\begin{itemize}

  \item Determined $\Gamma_{ee}$ from inclusive $\Upsilon$
    cross-section measurements with 1.5\% systematic uncertainties,
    and ratios of $\Gamma_{ee}$ with 0.8\% systematic uncertainties.

  \item This level of accuracy required detailed understanding of the
    detector.

  \item Planned and oversaw the acquisition of $\Upsilon$ scan data
    (2001--02).

\end{itemize}

  \item Dark Matter Sensitivity Study for a Future Linear Collider

\begin{itemize}

  \item Participated in a small group to study Linear Collider
  sensitivity to a cosmolog-ically-interesting mSUGRA model.

  \item Simplified chargino to $W^*$ LSP analysis and developed a
  method to fit $W^*$ distributions for the LSP mass.

\end{itemize}

  \item Silicon Vertex Detector and Drift Chamber Alignment for CLEO-III

\begin{itemize}

  \item Investigated track-biasing effects in bhabhas, mupairs, and
    cosmic rays, and numerically modelled my hypotheses of mechanical
    misalignments and distortions.  (Many were resolved.)

  \item Discovered a fine-angular scale effect in drift chamber
    tracking which is the limiting systematic in silicon alignment.

  \item Developed tools for alignment which balanced automated
    optimization with human evaluation of residuals distributions.

%%   \item Optimized alignment and hit-by-hit track-fitting weights used
%%     in CLEO-III.

%%   \item Transitioned alignment and fitting weight procedures from
%%     CLEO-III to \mbox{CLEO-c,} in which the Silicon Vertex Detector was
%%     replaced by a small wire chamber.

\end{itemize}

  \item Optimized Inner Cylinder Thickness for CLEO-c Vertex Detector (ZD).

\begin{itemize}

  \item Measured stress-strain dependence of prototype aluminum tubes
    on wall thickness to balance mechanical strength against radiation
    opacity.

\end{itemize}

  \item \hspace{-0.35 cm} \begin{tabular}{p{0.65\linewidth} r} \mbox{\hspace{0.45\linewidth}} & \mbox{\hspace{0.328\linewidth}} \\
Designed and built trigger and data acquisition system for a prototype \v Cerenkov detector. & REU, Summer 1998 \end{tabular}

\begin{itemize}

  \item Optimized photomultiplier base voltages, wrapped scintillator
    paddles, built a cosmic ray coincidence system, and finally built
    a trigger and data acquisition system using NIM electronics and an
    ADC/TDC card for the Macintosh.

  \item Used this system to calibrate the \v Cerenkov detector's
    response to high-$\beta$ muons.

  \item Undergraduate research project at Jefferson Lab under
    Bogdan Wojtsekhowski

\end{itemize}


\end{itemize}

\subsubsection*{Talks and Publications}

\begin{itemize}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.55\linewidth}} & \mbox{\hspace{0.237\linewidth}} \vspace{-0.4 cm} \\
$\Gamma_{ee}$ of $\Upsilon(1,2,3S)$ at Particles and Nuclei International Conference \mbox{\hspace{-0.79 cm}} & October 2005 \end{tabular}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.65\linewidth}} & \mbox{\hspace{0.237\linewidth}} \vspace{-0.4 cm} \\
$\Gamma_{ee}$ of $\Upsilon(1,2,3S)$ at Carg\`ese School of Physics and Cosmology & August 2003 \end{tabular}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.65\linewidth}} & \mbox{\hspace{0.315\linewidth}} \vspace{-0.4 cm} \\
$\Gamma_{ee}$ of $\Upsilon(1,2,3S)$ at American Physical Society & May 2002, May 2003 \end{tabular}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.65\linewidth}} & \mbox{\hspace{0.253\linewidth}} \vspace{-0.4 cm} \\
DAQ for prototype \v Cerenkov detector at APS Poster Session & May 1999 \end{tabular}

  \vspace{0.15 cm}

  \item Internal note on $\Gamma_{ee}$ which will be the basis for
    a reviewed publication

  \item Internal note on what the $\Upsilon$ lineshape scans teach us
    about storage ring parameters

  \item Internal note on alignment tools and how to apply them to the
    CLEO-c upgrade

  \item Co-authored internal note on CLEO-c vertex detector (ZD) design.

\end{itemize}

\subsubsection*{Teaching Experience}

\begin{itemize}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.65\linewidth}} & \mbox{\hspace{0.177\linewidth}} \vspace{-0.4 cm} \\
Supervised REU student working on spark chamber demonstration. & Summer 2004 \end{tabular}

  \item \hspace{-0.3 cm} \begin{tabular}{l r} \mbox{\hspace{0.65\linewidth}} & \mbox{\hspace{0.315\linewidth}} \vspace{-0.4 cm} \\
Teaching Assistant, Cornell Physics Department & Fall 1999 -- Fall 2000 \end{tabular}

  \vspace{0.15 cm}

  \item Presented hour-long lectures for the Mathematics graduate
  student seminar and the Society of Physics Students on FRW
  Cosmology, Bell's Inequality, Electromagnetic Gauge Freedom, the
  Higgs Mechanism, and Feynman Path Integrals.

  \item Guided innumerable tours of the CLEO detector and presented
  outreach talks to high school students and prospective graduate
  students.

\end{itemize}

\end{document}
